---
output: github_document
---

# boggler - Solve the Boggle Game

If there is one thing that programming tournaments taught me, it is that the first solution to try is brute force, so here is my solution.
From the Boggle board, it gets all the possible words, and then keeps only those that are contained in the dictionary.

Note that by running the code in parallel, I noticed a longer execution time. This is because parallelism can be done only at paths level, which are too many tasks and of too short execution.

## Installation

`boggler` is currently only available as a GitHub package.

To install it run the following from an R console:

```{r eval = FALSE}
if (!require("remotes")) {
  install.packages("remotes")
}
remotes::install_github("jcrodriguez1989/boggler", dependencies = TRUE)
```

## Usage

Create a random `3 x 3` boggle board:

```{r}
library("boggler")
set.seed(881918)

(act_board <- new_board(m = 3, n = 3, dices = en_boggle_dices))
```

And get all possible solutions:

```{r}
(boggle_sol <- solve(act_board, dict = spark_intro_dict, word_min_len = 2))
```

And calculate obtained points:

```{r}
get_points(boggle_sol[, 1])
```
